Awareness and Russellian Epistemology

### 2011-01-30 conclusions.tex
Fixed reference to Hintikka

Contrary to Hintikka's opposition, we have demonstrated various logics
where $\Box \phi$ has a Russellian interpretation: 
``$\phi$ may be derived logically from basic propositions that the
agent is aware of that $\phi$''.  This is accomplished
by first providing basic semantics, and then restricting ourselves to
classes of models which express the property we have labeled as 
$\textup{\textbf{CSQ}}_\vdash$, where $\vdash$ is some suitable
logic.  Our specification of what suitable means is minimal, although it
is enough to determine a complete notion of logical consequence in
every case.

>>>>

Contrary to Hintikka's opposition (as we presented in \S\ref{Hintikka}), we have demonstrated various logics
where $\Box \phi$ has a Russellian interpretation: 
``$\phi$ may be derived logically from basic propositions that the
agent is aware of that $\phi$''.  This is accomplished
by first providing basic semantics, and then restricting ourselves to
classes of models which express the property we have labeled as 
$\textup{\textbf{CSQ}}_\vdash$, where $\vdash$ is some suitable
logic.  Our specification of what suitable means is minimal, although it
is enough to determine a complete notion of logical consequence in
every case.
